Tables

### 2018-06-24 code/figures.rmd
Reorganized code files to improve clarity

```{r load data and packages}
library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data transformation
library(metafor) #To run meta-analyses
library(ggplot2) #Plot data
library(cowplot) #Combine several plots into one

dat <- read_csv("../data/collated_summary_data.csv")
```

```{r transformation_functions}
#Formulas found in: 
#Borenstein, M. (2009). Effect sizes for continuous data. In H. Cooper, L. V. Hedges, & J. C. Valentine (Eds.), The handbook of research synthesis and meta-analysis (2nd ed., pp. 221-235). New York: Russell Sage Foundation.

#For raw mean difference + SE
transform_SE <- function(ES, SE, n1, n2){ 
  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2)) #Borenstein, M. (2009). In Cooper & Hedges. p. 224
  d <- ES / sdpooled
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes. p.234
  r <- d / sqrt(d^2 + corr) #p.234
  data.frame(r = r, n = n1 + n2)
}

#For mean differrence + SD
transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #page 226. 
  d <- (m1 - m2) / sdpooled
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p.234
  r <- d / sqrt(d^2 + corr) #p. 234
  data.frame(r = r, n = n1 + n2)
}

#For Risk difference/OR
transform_RD <- function(ai, bi, ci, di){
  ai <- ifelse(ai == 0, 0.5, ai)  #If value is equal to zero add one half so as to not divide by zero
  bi <- ifelse(bi == 0, 0.5, bi)  #This affects 1 study for Allowed vs. forbidden
  ci <- ifelse(ci == 0, 0.5, ci)  #And several studies for Low vs. high category scales
  di <- ifelse(di == 0, 0.5, di)
  logOR <- log((ai*di) / (bi*ci)) #p. 266
  d = logOR * sqrt(3)/pi #p. 232
  n1 = ai + bi
  n2 = ci + di
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p. 234
  r <- d / sqrt(d^2 + corr) #p. 234
  data.frame(r = r, n = ai + bi + ci +di)
}

#No transformatin needed for correlation

transform_MA <- function(x){
  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    transformed <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)

    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){

     transformed <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)

    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){

     transformed <- transform_SD(x$outcome_t1, x$outcome_c1, x$outcome_t2, x$outcome_c2, x$ntreatment, x$ncontrol)

    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

  } else if(any(x[, "effect_type"] == "r")){

     transformed <- data.frame(r = x$effect_size, n = x$Ntotal)

    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

   } else{ #For the many labs OR that were transformed to d [double check]

     transformed <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)

}

  # data.frame(b = fit$b[[1]], I2 = fit$I2) #estimate out
  transformed
}

```{r transform_df}
#Transform effect sizes to raw correlations
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

@@

@@

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 6, label = "b = 3.81, R2 = 0.53", size = 3.5) +
  theme_classic()

@@

# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61
# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53
```

```{r labelled_plot, fig.asp= 0.618}
ggplot(res2, aes(x = z, y = I2, label = effect)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  geom_text(alpha = 0.5)
```

>>>>

```{r load packages, data and source helper functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(ggplot2)){install.packages("ggplot2")}
if(!require(cowplot)){install.packages("cowplot")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #Plot data
library(cowplot) #Combine several plots into one

dat <- read_csv("../data/collated_summary_data.csv")

source("helper_functions_tables_figures.r") #Load functions to prep data for figures
```

```{r transform_df}
#Transform effect sizes to raw correlations
#'transform_MA' is a sourced function
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

@@

# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61

@@

# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
  theme_classic()

@@

```{r robustness, results="hide"}
##Excluding anchoring effects
dropped_anchoring <- res2 %>%
  filter(!grepl("Anchoring", effect))

summary(lm(I2 ~ z, data = dropped_anchoring))
#b = 87.87, R2 = .51

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("temp_sim_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

dat3 <- dat3 %>% 
  bind_rows(.id = "effect") %>% #create dataframe with identifier
  select(I2, tau, effect) %>% 
  group_by(tau, effect) %>% 
  summarize(I2 = mean(I2)) %>% #Take mean of I2 at each tau-level and for each effect
  ungroup()

#combined line plot gives good overview. Point version of the same is also interesting.
ggplot(dat3, aes(x = tau, y = I2, group = effect)) +
  geom_line(alpha = 0.4) +
  theme_bw() +
  scale_x_continuous(minor_breaks = NULL) +
  scale_y_continuous(minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100))

```{r Density_plot, fig.asp= 0.618}
dens <- readRDS("temp_sim_results_2.RDS")
names(dens) <-  sort(unique(dat$effect))

#Simulated data at various heterogeneity levels, prep for plotting
I2_dist <- dens %>% 
  bind_rows(.id = "effect") %>% 
  rename(heterogeneity = tau_index) %>% 
  mutate(heterogeneity = recode(heterogeneity,
                            '1' = "Zero",
                            '2' = "Small",
                            '3' = "Medium",
                            '4' = "Large"),
         heterogeneity = as.factor(heterogeneity))

#Observed I2 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'est_heterogeen_smd_raw'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
  select(effect, I2 = s_I2) %>%
  mutate(heterogeneity = "Observed")

ggplot(I2_dist, aes(x = I2, group = heterogeneity, fill = heterogeneity, linetype = heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 50, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"), breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_color_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed"))

### 2018-06-24 code/tables.rmd
Reorganized code files to improve clarity

```{r load data and packages}
library(readr)
library(dplyr)
library(kableExtra)
library(purrr)
library(metafor)

dat <- read_csv("../data/collated_summary_data.csv")
```

@@

est_heterogen_smd_raw <- function(x){
  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){

    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)

  } else if(any(x[, "effect_type"] == "Raw mean difference")){

    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){

    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "effect_type"] == "r")){

    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)

  } else{ #for all two-group count effects

    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

  }

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
}

#Apply function to data
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date

OR <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR

#Add rs to the data-frame
het <- dat %>% 
  select(rs, Site, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  select(rs, effect,k , everything()) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
```

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
library(kableExtra)

het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Size", "I2(%)", "ci.lb", "ci.ub")) %>% 
  kable_styling("scale_down") %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors. Standardized mean difference is Hedge's g. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. Effects were estimated in metafor using REML with the 'knha' correction. RS = Replication Study, k = no. primary studies, Size = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.")

>>>>

```{r load packages, data and source functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(kableExtra)){install.packages("kableExtra")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(kableExtra) #For creating good-looking pdf tables

dat <- read_csv("../data/collated_summary_data.csv")

source("helper_functions_tables_figures.r") #Load functions to prep data for figures
```

@@

#fit a random effects model to all empirical data
#Each set of input datapoints is meta-analyzed as per the original replication project
#Function 'est_heterogen_smd_raw' is sourced
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date

#Add rs and k to the data-frame and prep for table
het <- dat %>% 
  select(rs, Site, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD"))

#Load simulation results (power/type 1 error for all effects)
dens <- readRDS("temp_sim_results_2.RDS")
names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

#Summary of simulation results, needs to be combined with main part of table
I2_ci_lb <- dens %>% 
  bind_rows(.id = "effect") %>% 
  group_by(effect, tau_index) %>% 
  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
  ungroup() %>% 
  tidyr::spread(key = tau_index, value = power) %>% #prep for table
  rename(zero = '1', small = '2', medium = '3', large = '4')

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_ci_lb) %>% 
  select(rs, effect,k , everything()) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
```

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
#library(kableExtra)

het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 8, "Heterogeneity & power/type 1" = 4)) %>% 
  kable_styling("scale_down", font_size = 8) %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = " Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RS = Replication Study, k = no. primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. (OSF.io/XXXX)")
